---
title: "DataMunging PPT"
author: "Melvin Adkins, Raymond Blaha, Paul Hwang, Stephanie Diaz Ortega"
output: ioslides_presentation
fontsize: 12pt
---

## IMDB Top 250 Movies

- Set of 250 movie data from IMDB
- (https://www.kaggle.com/datasets/yehorkorzh/imdb-top-250-movies)

```{r, echo = FALSE, results=FALSE, message=FALSE, warning=FALSE, comment=FALSE, cache = TRUE}
library(data.table)

## Loading Data
data.wide <- "C:\\Users\\pauld\\OneDrive\\Desktop\\Data Munging\\Final Project\\DataMungingProject\\MovieCleanFull.csv"
movie.wide <- fread(data.wide)

```

## Variables

### Numeric
- Num, Year, Released, Runtime, Metascore, imdbRating, imdbVote, imdbID

### Text
- Title, Genre, Director, Writer, Actor, Plot, Language, Country, Awards, Type, DVD, BoxOffice, Production, Websites

## DataMunging Pt1

### Type Modification

- Runtime -> "123min"
- BoxOffice -> "$1,234,567"
- imdbVoting -> "1,234,567"

## DataMunging Pt2

### Data Split
- Genre -> "Drama, Action"
- Actor -> "Tim Robbins, Morgan Freeman"
- Writer -> "Mario Puzo (screenplay)"
- Language -> "English, Italian, Latin"
- Country -> "USA, UK"
- Awards -> "Won 3 Oscars. Another 23 wins & 27 nominations."

## DataMunging Pt3

### Removed
- Released
- Plot
- imdbID
- Type
- DVD
- Website

## DataMunging Pt4

### Consistency and Completeness
```{r, echo = FALSE, message=FALSE, cache=TRUE}
#1-colSums(is.na(df)/lengths(df))
cc <- 1-colSums(is.na(movie.wide)/lengths(movie.wide))
cc

```

## Exploratory Data Analysis

### 1D Analysis

- Observe characteristics of single variable
- Present all included variables

## Year
- Mean: 1982.676, SD: 24.80921

```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
library(ggplot2)
library(cowplot)

# mean(movie.wide$Year)
# sd(movie.wide$Year)

gp <- ggplot(data = movie.wide, aes(x = Year)) + 
  geom_histogram(color = "black", fill = "lightblue") +
  scale_y_continuous(limits= c(0,25), expand = c(0,0)) +
  theme_light()
gp2 <- ggplot(data = movie.wide, aes(x = Year)) + 
  geom_boxplot(color = "black", fill = "lightblue") +
  theme_void()
plot_grid(gp, gp2, ncol = 1, align = "v", rel_heights = c(4,1), axis = "lr")

# ggplot(data = movie.wide, aes(x = Year)) + 
#   geom_histogram(aes(y = ..density..), color = "black", fill = "lightblue") + 
#   geom_density(alpha = 0.1, fill = "red") +
#   scale_y_continuous(limits= c(0,0.03), expand = c(0,0)) +
#   theme_light()
```

## Runtime
- Mean: 126.808, SD: 29.76338

```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
# mean(movie.wide$Runtime)
# sd(movie.wide$Runtime)

gp <- ggplot(data = movie.wide, aes(x = Runtime)) + 
  geom_histogram(color = "black", fill = "lightblue") +
  scale_y_continuous(limits= c(0,25), expand = c(0,0)) +
  theme_light()
gp2 <- ggplot(data = movie.wide, aes(x = Runtime)) + 
  geom_boxplot(color = "black", fill = "lightblue") +
  theme_void()
plot_grid(gp, gp2, ncol = 1, align = "v", rel_heights = c(4,1), axis = "lr")

# ggplot(data = movie.wide, aes(x = Runtime)) + 
#   geom_histogram(aes(y = ..density..), color = "black", fill = "lightblue") + 
#   geom_density(alpha = 0.1, fill = "red") +
#   scale_y_continuous(limits= c(0,0.02), expand = c(0,0)) +
#   theme_light()
```


## Directors Pt1
- Unique Directors: 155
```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
library(plotly)
library(plyr)

# length(unique(movie.wide$Director))

table.dir <- plyr::count(movie.wide$Director)
gp <- ggplot(data = movie.wide, aes(x=Director)) +
  geom_bar(stat = "count",color = "black", fill = "lightblue")
ggplotly(gp)
```

## Directors Pt2
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE, null_prefix = TRUE}
new.table <- table.dir[table.dir$freq > 3,]
new.table
```

## Directors Pt3
```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
gp2 <- ggplot(data = table.dir[table.dir$freq > 3,], aes(x=x, y=freq)) +
  geom_bar(stat = "identity",color = "black", fill = "lightblue") +
  theme(axis.text.x = element_text(angle = 90)) + xlab("Directors")
ggplotly(gp2)
```


## Writers Pt1
- Unique Writers: 213

```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
# length(unique(movie.wide$Writer))

table.wri <- plyr::count(movie.wide$Writer)
gp <- ggplot(data = table.wri, aes(x=x, y=freq)) +
  geom_bar(stat = "identity", color = "black", fill = "lightblue")
# ggplotly(gp)

table.wri[table.wri$freq > 3,]
gp2 <- ggplot(data = table.wri[table.wri$freq > 3,], aes(x=x, y=freq)) +
  geom_bar(stat = "identity", color = "black", fill = "lightblue") + xlab("Writers")
ggplotly(gp2)
```

## Writers Pt2
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
gp2 <- ggplot(data = table.wri[table.wri$freq > 3,], aes(x=x, y=freq)) +
  geom_bar(stat = "identity", color = "black", fill = "lightblue") + xlab("Writers")
ggplotly(gp2)
```


## Metascore
- Mean: 80.0452, SD: 11.03034
```{r, echo=FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
# mean(movie.wide$Metascore, na.rm = TRUE)
# sd(movie.wide$Metascore, na.rm = TRUE)

gp <- ggplot(data = movie.wide, aes(x = Metascore)) + 
  geom_histogram(color = "black", fill = "lightblue") +
  scale_y_continuous(limits= c(0,15), expand = c(0,0)) +
  theme_light()
gp2 <- ggplot(data = movie.wide, aes(x = Metascore)) + 
  geom_boxplot(color = "black", fill = "lightblue") +
  theme_void()
plot_grid(gp, gp2, ncol = 1, align = "v", rel_heights = c(4,1), axis = "lr")

# ggplot(data = movie.wide, aes(x = Metascore)) + 
#   geom_histogram(aes(y = ..density..), color = "black", fill = "lightblue") + 
#   geom_density(alpha = 0.1, fill = "red") +
#   scale_y_continuous(limits= c(0,0.05), expand = c(0,0)) +
#   theme_light()
```

## imbdRating
- Mean: 8.244, SD: 0.2457347
```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
# mean(movie.wide$imdbRating)
# sd(movie.wide$imdbRating)

gp <- ggplot(data = movie.wide, aes(x = imdbRating)) + 
  geom_histogram(color = "black", fill = "lightblue") +
  scale_y_continuous(limits= c(0,40), expand = c(0,0)) +
  theme_light()
gp2 <- ggplot(data = movie.wide, aes(x = imdbRating)) + 
  geom_boxplot(color = "black", fill = "lightblue") +
  theme_void()

plot_grid(gp, gp2, ncol = 1, align = "v", rel_heights = c(4,1), axis = "lr")

# ggplot(data = movie.wide, aes(x = imdbRating)) + 
#   geom_histogram(aes(y = ..density..), color = "black", fill = "lightblue") + 
#   geom_density(alpha = 0.1, fill = "red") +
#   scale_y_continuous(limits= c(0,7.5), expand = c(0,0)) +
#   theme_light()
```


## imbdVotes
- Mean: 431401.3, SD: 367703.3
```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
# mean(movie.wide$imdbVotes, na.rm = TRUE)
# sd(movie.wide$imdbVotes, na.rm = TRUE)

gp <- ggplot(data = movie.wide, aes(x = imdbVotes)) + 
  geom_histogram(color = "black", fill = "lightblue") +
  scale_y_continuous(limits= c(0,30), expand = c(0,0)) +
  theme_light()
gp2 <- ggplot(data = movie.wide, aes(x = imdbVotes)) + 
  geom_boxplot(color = "black", fill = "lightblue") +
  theme_void()
plot_grid(gp, gp2, ncol = 1, align = "v", rel_heights = c(4,1), axis = "lr")

# ggplot(data = movie.wide, aes(x = imdbVotes)) + 
#   geom_histogram(aes(y = ..density..), color = "black", fill = "lightblue") + 
#   geom_density(alpha = 0.1, fill = "red") +
#   theme_light()
```

## boxoffice
- Mean: 158727934, SD: 169133912
```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
# mean(movie.wide$BoxOffice, na.rm = TRUE)
# sd(movie.wide$BoxOffice, na.rm = TRUE)

gp <- ggplot(data = movie.wide, aes(x = BoxOffice)) + 
  geom_histogram(color = "black", fill = "lightblue") +
  scale_y_continuous(limits= c(0,15), expand = c(0,0)) +
  theme_light()
gp2 <- ggplot(data = movie.wide, aes(x = BoxOffice)) + 
  geom_boxplot(color = "black", fill = "lightblue") +
  theme_void()
plot_grid(gp, gp2, ncol = 1, align = "v", rel_heights = c(4,1), axis = "lr")

# ggplot(data = movie.wide, aes(x = BoxOffice)) + 
#   geom_histogram(aes(y = ..density..), color = "black", fill = "lightblue") + 
#   geom_density(alpha = 0.1, fill = "red") +
#   theme_light()
```

## Production Pt1
- Unique Productions: 89
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
# length(unique(movie.wide$Production))

table.pro <- plyr::count(movie.wide$Production)
gp <- ggplot(data = table.pro, aes(x=x, y=freq)) +
  geom_bar(stat = "identity", color = "black", fill = "lightblue")
ggplotly(gp)
```

## Production Pt2
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
table.pro[table.pro$freq > 3,]
```

## Production Pt3
```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
gp2 <- ggplot(data = table.pro[table.pro$freq > 3,], aes(x=x, y=freq)) +
  geom_bar(stat = "identity", color = "black", fill = "lightblue") +
  theme(axis.text.x = element_text(angle = 90)) + xlab("production")
ggplotly(gp2)
```

## Actors and Actress Pt1
- Actors and Actress: 773
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
library(tidyr)
actors.data <- movie.wide[,c("First Actor", "Second Actor", "Third Actor", "Fourth Actor")]
actors <- actors.data %>% pivot_longer(
  cols=c("First Actor", "Second Actor", "Third Actor", "Fourth Actor"),
  names_to = "Actors Type",
  values_to = "Actor"
)

# length(unique(actors$Actor))

table.act <- plyr::count(actors$Actor)
gp <- ggplot(data = table.act, aes(x=x, y=freq)) +
  geom_bar(stat = "identity", color = "black", fill = "lightblue")
# ggplotly(gp)

head(table.act[table.act$freq > 3,])

# gp2 <- ggplot(data = table.act[table.act$freq > 3,], aes(x=x, y=freq)) +
#   geom_bar(stat = "identity", color = "black", fill = "lightblue") +
#   theme(axis.text.x = element_text(angle = 90))
# ggplotly(gp2)
```

## Actors and Actress Pt2
```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
gp2 <- ggplot(data = table.act[table.act$freq > 3,], aes(x=x, y=freq)) +
  geom_bar(stat = "identity", color = "black", fill = "lightblue") +
  theme(axis.text.x = element_text(angle = 90)) + xlab("Actors and Actresses")
ggplotly(gp2)
```

## Awards Pt1
- Mean: 29.44, SD: 40.12799
```{r, echo = FALSE, warning=FALSE, comment = FALSE, cache = TRUE, message=FALSE}
# mean(movie.wide$Awards, na.rm = TRUE)
# sd(movie.wide$Awards, na.rm = TRUE)

gp <- ggplot(data = movie.wide, aes(x = Awards)) + 
  geom_histogram(color = "black", fill = "lightblue") +
  scale_y_continuous(limits= c(0,30), expand = c(0,0)) +
  theme_light()
# ggplotly(gp)

gp2 <- ggplot(data = movie.wide, aes(x = Awards)) + 
  geom_boxplot(color = "black", fill = "lightblue") +
  theme_void()
plot_grid(gp, gp2, ncol = 1, align = "v", rel_heights = c(4,1), axis = "lr")

# ggplot(data = movie.wide, aes(x = Awards)) + 
#   geom_histogram(aes(y = ..density..), color = "black", fill = "lightblue") + 
#   geom_density(alpha = 0.1, fill = "red") +
#   theme_light()
```

## Awards Pt2
- 28 movies with 75 awards or more
```{r, echo = FALSE, warning = FALSE, cache = TRUE, message=FALSE}
head(movie.wide[movie.wide$Awards > 75 ,c("Title", "Awards", "imdbRating")])
```


## Nominations Pt1
- Mean: 40.308, SD: 52.18792
```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
# mean(movie.wide$Nominations, na.rm = TRUE)
# sd(movie.wide$Nominations, na.rm = TRUE)

gp <- ggplot(data = movie.wide, aes(x = Nominations)) + 
  geom_histogram(color = "black", fill = "lightblue") +
  scale_y_continuous(limits= c(0,30), expand = c(0,0)) +
  theme_light()
# ggplotly(gp)

gp2 <- ggplot(data = movie.wide, aes(x = Nominations)) + 
  geom_boxplot(color = "black", fill = "lightblue") +
  theme_void()
plot_grid(gp, gp2, ncol = 1, align = "v", rel_heights = c(4,1), axis = "lr")

# ggplot(data = movie.wide, aes(x = Nominations)) + 
#   geom_histogram(aes(y = ..density..), color = "black", fill = "lightblue") + 
#   geom_density(alpha = 0.1, fill = "red") +
#   theme_light()
```

## Nominations Pt2
- 25 movies with 120 nominations or more
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
head(movie.wide[movie.wide$Nominations > 120,c("Title", "Nominations", "imdbRating")])
```

## Awards and Nominations Pt1
- 34 movies with 75+ awards or 120+ nominations
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
## showing deviations for awards and nominations
head(movie.wide[movie.wide$Awards > 75 | movie.wide$Nominations > 120,
           c("Title", "Awards", "Nominations", "imdbRating")])
```

## Awards and Nominations Pt2
- 19 movies with 75+ awards and 120+ nominations
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
## showing deviations for awards and nominations
head(movie.wide[movie.wide$Awards > 75 & movie.wide$Nominations > 120,
           c("Title", "Awards", "Nominations", "imdbRating")])
```

## Awards and Nominations Pt3
- 9 movies with 75+ awards and 120- nominations
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
## showing deviations for awards and nominations
movie.wide[movie.wide$Awards > 75 & movie.wide$Nominations < 120,
           c("Title", "Awards", "Nominations", "imdbRating")]
```

## Awards and Nominations Pt4
- 6 movies with 75- awards and 120+ nominations
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
## showing deviations for awards and nominations
movie.wide[movie.wide$Awards < 75 & movie.wide$Nominations > 120,
           c("Title", "Awards", "Nominations", "imdbRating")]
```



## Genre
- Unique Genres: 24
```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
genre.data <- movie.wide[,c("First Genre", "Second Genre", "Third Genre")]
genres <- genre.data %>% pivot_longer(
  cols=c("First Genre", "Second Genre", "Third Genre"),
  names_to = "Genre Type",
  values_to = "Genre"
)

# length(unique(genres$Genre))

table.gen <- na.omit(plyr::count(genres$Genre))

gp <- ggplot(data = table.gen, aes(x=x, y=freq)) +
  geom_bar(stat = "identity", color = "black", fill = "lightblue") +
  scale_y_continuous(limits = c(0,180), expand = c(0,0)) +
  theme(axis.text.x = element_text(angle = 90)) + xlab("Genres")
ggplotly(gp)
```

## Language Pt1
- Unique Language: 44
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
lang.data <- movie.wide[,c("l1","l2","l3","l4","l5","l6","l7")]
language <- lang.data %>% pivot_longer(
  cols=c("l1","l2","l3","l4","l5","l6","l7"),
  names_to = "Language Type",
  values_to = "Language"
)

# length(unique(language$Language))

table.lang <- na.omit(plyr::count(language$Language))

gp <- ggplot(data = table.lang, aes(x=x, y=freq)) +
  geom_bar(stat = "identity", color = "black", fill = "lightblue") +
  scale_y_continuous(limits = c(0,260), expand = c(0,0)) +
  theme(axis.text.x = element_text(angle = 90))
# ggplotly(gp)

table.lang[table.lang$freq > 3,]
```



## Language Pt2
```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
gp2 <- ggplot(data = table.lang[table.lang$freq > 3,], aes(x=x, y=freq)) +
  geom_bar(stat = "identity", color = "black", fill = "lightblue") +
  scale_y_continuous(limits = c(0,260), expand = c(0,0)) + 
  theme(axis.text.x = element_text(angle = 90)) + xlab("Language")
ggplotly(gp2)
```

## Country Pt1
- Unique Countries: 31
```{r, echo = FALSE, warning=FALSE, cache = TRUE, message=FALSE}
coun.data <- movie.wide[,c("c1","c2","c3","c4","c5","c6","c7","c8","c9")]
country <- coun.data %>% pivot_longer(
  cols=c("c1","c2","c3","c4","c5","c6","c7","c8","c9"),
  names_to = "Country Type",
  values_to = "Country"
)

# length(unique(country$Country))

table.coun <- na.omit(plyr::count(country$Country))
# gp <- ggplot(data = table.coun, aes(x=x, y=freq)) +
#   geom_bar(stat = "identity", color = "black", fill = "lightblue") +
#   scale_y_continuous(limits = c(0,260), expand = c(0,0)) + 
#   theme(axis.text.x = element_text(angle = 90))
# ggplotly(gp)

table.coun[table.coun$freq > 3,]
```

## Country Pt2
```{r, echo = FALSE, warning=FALSE, comment=FALSE, cache = TRUE, message=FALSE}
gp2 <- ggplot(data = table.coun[table.coun$freq > 3,], aes(x=x, y=freq)) +
  geom_bar(stat = "identity", color = "black", fill = "lightblue") +
  scale_y_continuous(limits = c(0,260), expand = c(0,0)) +
  theme(axis.text.x = element_text(angle = 90))
ggplotly(gp2)
```


## Number of Awards, BoxOffice, and imbdRatings Pt1

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(plotly)
mag1 <- ggplot(movie.wide, aes(x = BoxOffice, y = Awards, color = Metascore, label1 = Title, label2=Year, label3=movie.wide$'First Genre', label4=movie.wide$'Second Genre', label5=movie.wide$'Third Genre')) + 
  geom_point() +
  geom_hline(yintercept = 29.44, linetype = "dashed", color = "blue") +
  geom_vline(xintercept = mean(movie.wide$BoxOffice, na.rm=TRUE), 
             linetype = "dashed", color = "blue")
ggplotly(mag1)
```

<!-- - Top Left Region  -->
<!-- - Films of the imdb Top 250 list which had above avg Awards (29) but below avg Box Office (159M) -->
<!-- - Those films also show lighter shade of points => higher Metascore ratings -->
<!-- - Range of Year: 1994-2017  -->
<!-- - We might expect movies with high Award counts to have higher Box Office  -->


## Number of Awards, BoxOffice, and imbdRatings Pt2


<!-- * Top Left Region -->
<!-- * Films show darker shades of blue => lower ratings with respect to imdb ratings -->
<!-- * Indicates differences in how people rate between imdb and Metascore -->
<!-- * Range of Year: 1994-2017 -->
<!-- * Films with Biography or Drama as first genre were mostly clustered in this region -->

```{r, echo = FALSE, message=FALSE, warning=FALSE}
mag2 <- ggplot(movie.wide, aes(x = BoxOffice, y = Awards, color = imdbRating, label1=Title, label2=Year, shape=movie.wide$'First Genre', lable3=movie.wide$'Second Genre', label4=movie.wide$'Third Genre')) + geom_point() +
  geom_hline(yintercept = 29.44, linetype = "dashed", color = "blue") +
  geom_vline(xintercept = mean(movie.wide$BoxOffice, na.rm=TRUE), linetype = "dashed", color = "blue") 
ggplotly(mag2)
```

## Nominations and imdbRatings

<!-- - Showing the relationship between Nominations and imdbRatings. Seems to be flat overall.  -->
<!-- - Seems that most Nominations that have occurred are with imdbRatings between 8.2-8.5. -->
<!-- - Range was for all movies from 1900-2019.  -->

```{r, echo = FALSE, warning = FALSE, comment=FALSE, message=FALSE}
#Creating a plot with lm, to show the relationship between nominations and imdbRatings. 
ImdbRatingplot <- ggplot(movie.wide, aes(x = Nominations, y = imdbRating)) + geom_point() + geom_smooth(method = "lm") + labs(title = "Nominations vs imdbRating", x = "Nominations", y = "imdbRating") + theme(plot.title = element_text(hjust = 0.5))
ImdbRatingplot
```

## Nominations and Year

<!-- - Showing the relationship between Nominations and Year of movie release.  -->
<!-- - Nominations for movies exploded around the 1990's. Where we see the first instance of a movie receiving 100 nominations.  -->
<!-- - Range is from 1900 to 2019.  -->
<!-- - We also see an instance where a movie has over 300 nominations.  -->
```{r, echo = FALSE, warning = FALSE, comment=FALSE, message=FALSE}
#Creating a plot with lm, to show the relationship between year and nominations.
Nominationsplot <- ggplot(movie.wide, aes(x = Year, y = Nominations)) + geom_point() + geom_smooth(method = "lm") + labs(title = "Year vs Nominations", x = "Year", y = "Nominations") + theme(plot.title = element_text(hjust = 0.5))
Nominationsplot
```

## Nominations and imdbRatings Pt3

<!-- - X-Axis as imdbRating -->
<!-- - Y-Axis as imdbVotes -->
<!-- - Z-Axis as Nominations -->
<!-- - Confirms what we have been seeing regarding that the most Nominations that are given to movies are ones that are within the 8.25-8.50 imdbRating.  -->
```{r, echo = FALSE, warning = FALSE, comment=FALSE, message = FALSE}
#install.packages("plotly")
#install.packages("ggplot2")
#install.packages("tidyverse")
#install.packages("cowplot")
#install.packages("dplyr")
library("dplyr")
library("ggplot2")
library("plotly")
movie.wide %>%
    sample_n(100) %>%
    plot_ly(
        x = ~ imdbRating,
        y = ~ imdbVotes,
        z = ~ Nominations,
        color = ~imdbRating,
        size = ~80,
        text = ~paste("Title:", Title, "<br>imdbRating:", imdbRating, "<br>imdbVotes:", imdbVotes, "<br>Nominations:", Nominations),
        aplha = 0.5,
        type = "scatter3d",
        mode = "markers")
```

## IMDB Ratings and Production Company

```{r, echo = FALSE, warning = FALSE, message = FALSE}
gg1 <- ggplot(movie.wide = movie.wide$Title, mapping = aes(x = movie.wide$imdbRating, y = movie.wide$Production)) + geom_col()
ggplotly(gg1)
```


## Awards and Production

```{r, echo = FALSE, warning = FALSE, message = FALSE}
gg1 <- ggplot(movie.wide = movie.wide$Title, mapping = aes(x = movie.wide$Awards, y = movie.wide$Production)) + geom_col() + geom_bar(stat="identity", color="white") + theme_minimal()
ggplotly(gg1)
```


## Correlation Pt 1

```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE}
library(corrplot)
## intro graphics with correlation
movie.numeric <- movie.wide[,c("Year", "Runtime", "Metascore", "imdbRating", 
                               "imdbVotes", "BoxOffice", "Awards", "Nominations")]
res <- cor(movie.numeric, use = "pairwise.complete.obs")
res
```

## Correlation Pt 2

```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE}
corrplot(res, type = "full", order = "original", t1.srt = 45)
```

## ImdbRating and MetaScore

```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE, results='hide'}
cor(movie.wide$imdbRating, movie.wide$Metascore, use = "pairwise.complete.obs")
```
- Correlation Coefficient: 0.172

```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE}
ggplot(data = movie.wide, aes(y=imdbRating, x= Metascore)) + geom_point() + 
  geom_smooth() + theme_bw()
```


## ImdbRating and Year

- Correlation Coefficient: 0.045
```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE, results='hide'}
cor(movie.wide$imdbRating, movie.wide$Year, use = "pairwise.complete.obs")
```

```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE}
ggplot(data = movie.wide, aes(y=imdbRating, x= Year)) + geom_point() + 
  geom_smooth() + theme_bw()
```

## ImdbRating and Runtime

- Correlation Coefficient: 0.248
```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE, results='hide'}
cor(movie.wide$imdbRating, movie.wide$Runtime, use = "pairwise.complete.obs")
```

```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE}
ggplot(data = movie.wide, aes(y=imdbRating, x= Runtime)) + geom_point() + 
  geom_smooth() + theme_bw()
```


## ImdbRating and ImdbVotes

- Correlation Coefficient: 0.657
```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE, results='hide'}
cor(movie.wide$imdbRating, movie.wide$imdbVotes, use = "pairwise.complete.obs")
```

```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE}
ggplot(data = movie.wide, aes(y=imdbRating, x= imdbVotes)) + geom_point() + 
  geom_smooth() + theme_bw()
```

## ImdbRating and BoxOffice

- Correlation Coefficient: 0.657
```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE, results='hide'}
cor(movie.wide$imdbRating, movie.wide$BoxOffice, use = "pairwise.complete.obs")
```

```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE}
ggplot(data = movie.wide, aes(y=imdbRating, x= BoxOffice)) + geom_point() + 
  geom_smooth() + theme_bw()
```

## ImdbRating and Awards

- Correlation Coefficient: 0.200
```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE, results='hide'}
cor(movie.wide$imdbRating, movie.wide$Awards, use = "pairwise.complete.obs")
```

```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE}
ggplot(data = movie.wide, aes(y=imdbRating, x= Awards)) + geom_point() + 
  geom_smooth() + theme_bw()
```


## ImdbRating and Nominations

- Correlation Coefficient: 0.082
```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE, results='hide'}
cor(movie.wide$imdbRating, movie.wide$Nominations, use = "pairwise.complete.obs")
```

```{r, warning=FALSE, echo=FALSE, message=FALSE, cache=TRUE}
ggplot(data = movie.wide, aes(y=imdbRating, x= Nominations)) + geom_point() + 
  geom_smooth() + theme_bw()
```

## ImdbRatings and Genre

```{r, cache=TRUE, message=FALSE, echo=FALSE, results='hide'}
## using long form for genre only
movie.genre <- movie.wide %>% pivot_longer(
  cols=c("First Genre", "Second Genre", "Third Genre"),
  names_to = "Genre Type",
  values_to = "Genre")
movie.genre <- movie.genre[!is.na(movie.genre$Genre),]
```

```{r, cache=TRUE, message=FALSE, echo=FALSE}
gp <- ggplot(data = movie.genre, aes(x = imdbRating, fill = Genre)) + 
  geom_histogram(color = "black") +
  scale_y_continuous(limits= c(0,100), expand = c(0,0)) +
  theme_light()
ggplotly(gp)
```


## Questions

## Thank You
