---
title: "DataMungingProjectMovies"
output: html_document
date: "2022-12-05"
---

TALKING POINTS:
IMDb DOB Oct. 1990

"...Even the vaunted IMDb Top 250 — nominally the best-liked films ever — is worth taking with 250 grains of salt."--to quote Walt Hickey

How much trust do you put on ImDB ratings?
--Should you? 
--What if someone abosolutely hates Tom Hiddleston? or Henry Cavill?
--What about movies from the 50's, 60's,...?
--What is the distribution of the data? 
--demographics


Observations:
--Warner Bros. has the highest ratings and the most awards.
--Disney doesn't get much recognition in this area. 
--Production companies with lower (and by low we mean 8.0) ratings collectively, have quite a few awards.
--Is the population harsher than the Academy?
 Popolation mean number of votes: 431401.3
 voters in the Academy: 9,427 as of Dec 2020
--

The woes of missing data:
--Where do the awards come from? 
--Academy awards? BAFTA? Golden Globe?
--demographics of voters: age, sex, etc...
--movies with ratings lower than 8.0 for comparison











#IMBD Ratings of movies Vs Production Company

```{r}
ggplot(MovieCleanFull = MovieCleanFull$Title, mapping = aes(x = MovieCleanFull$imdbRating, y = MovieCleanFull$Production)) + geom_col()
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
ggplot(MovieCleanFull = MovieCleanFull$Title, mapping = aes(x = MovieCleanFull$imdbRating, y = MovieCleanFull$Production, MovieCleanFull$Writer)) + geom_col()
```




#ImBD Ratings vs Writers
```{r}
ggplot(MovieCleanFull = MovieCleanFull$Title, mapping = aes(x = MovieCleanFull$imdbRating, y = MovieCleanFull$Writer)) + geom_col()
```

Function for completeness and consistency 
```{r}
#1-colSums(is.na(df)/lengths(df))

1-colSums(is.na(MovieCleanFull)/lengths(MovieCleanFull))
```



barplot(table(MovieCleanFull$Title), col=c("lightblue","darkred"),main="Low (0) vs. High (1) Temp",ylab="Count",horiz=T)

table(MovieCleanFull$Title)
sort(MovieCleanFull$Title(MovieCleanFull$ImdbRating), decreasing = TRUE)



```{r}
cor(MovieCleanFull$imdbRating, MovieCleanFull$Runtime)
```
```{r}
plot(MovieCleanFull$imdbRating, MovieCleanFull$Runtime)
```

```{r}
ggplot(MovieCleanFull = MovieCleanFull$Title, mapping = aes(x = MovieCleanFull$Awards, y = MovieCleanFull$Production)) + geom_col()
```


```{r}
ggplot(MovieCleanFull = MovieCleanFull$Title, mapping = aes(x = MovieCleanFull$Awards, y = MovieCleanFull$Production)) + geom_col() + geom_bar(stat="identity", color="white") + theme_minimal()
```



```{r}
cor(MovieCleanFull$Awards, MovieCleanFull$imdbRating)
```
```{r}
plot(MovieCleanFull$Awards, MovieCleanFull$imdbRating)
```

